---
title: "DS 202 Lab 2"
author: "Haley Braun"
date: "9/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
boxplot(choco$Rating)
```
1. How are ratings distributed? Don't forget to mention outliers, if there are any.
  Dirstibuted from around 2-4 and there is an outlier near 5 and below 2

2. Do ratings depend on the cacao percentage of a chocolate bar? 
  No there does not because there isnt a correlation across all of the data.
```{r, eval=FALSE}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
plot(choco$Cocoa.Pct,choco$Rating, xlab = "Rating", ylab = "Cocoa Percent", main = "Cocao percent compared to Rating")
cor(choco$Cocoa.Pct,choco$Rating)
```
3. What class is the variable representing company locations? How is this different from a 'character' variable? (You do not need to produce a graphic for this question.)
  Its a factor.